Squintability and Other Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimization Choices

### 2025-03-05 jso.qmd
reference in the conclusion

Future work can focus on developing more efficient optimization algorithm for
noise indexes with low squintability metric, which resemble a needle-in-a-haystack 
problem. Additionally, if the index function is differentiable, automatic 
differentiation can be used to implement new gradient-based optimizers.

>>>>

Future work can focus on developing more efficient optimization algorithm for
noise indexes with low squintability metric, which resemble a needle-in-a-haystack 
problem [@siemenn2023fast]. Additionally, if the index function is differentiable, automatic 
differentiation can be used to implement new gradient-based optimizers [@prince2023understanding].

### 2025-03-05 jso.tex
reference in the conclusion

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacityback=0, coltitle=black, titlerule=0mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, leftrule=.75mm, breakable, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, rightrule=.15mm, bottomrule=.15mm, toprule=.15mm, left=2mm, colback=white]

@@

\toprule
\textbf{Characteristic} & \textbf{OR} \textbf{(95\% CI)}\textsuperscript{\textit{1}} & \textbf{p-value} \\ 
\midrule\addlinespace[2.5pt]
Smoothness & 1.01 (0.92 to 1.11) & 0.810 \\ 
Squintability & 1.23 (1.12 to 1.38) & \textbf{<0.001} \\ 
Dimension & 0.58 (0.45 to 0.73) & \textbf{<0.001} \\ 
Number of jellyfish & 1.32 (1.17 to 1.50) & \textbf{<0.001} \\ 
Maximum number of iterations & 1.06 (0.94 to 1.20) & 0.328 \\ 
\bottomrule

@@

Future work can focus on developing more efficient optimization
algorithm for noise indexes with low squintability metric, which
resemble a needle-in-a-haystack problem. Additionally, if the index
function is differentiable, automatic differentiation can be used to
implement new gradient-based optimizers.

@@

@@

>>>>

\begin{tcolorbox}[enhanced jigsaw, breakable, titlerule=0mm, coltitle=black, colframe=quarto-callout-note-color-frame, rightrule=.15mm, bottomtitle=1mm, colback=white, opacityback=0, leftrule=.75mm, opacitybacktitle=0.6, toprule=.15mm, left=2mm, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, colbacktitle=quarto-callout-note-color!10!white, bottomrule=.15mm]

@@

\toprule
\textbf{Characteristic} & \textbf{OR} \textbf{(95\% CI)}\textsuperscript{\textit{1}} & \textbf{p-value} \\ 
\midrule\addlinespace[2.5pt]
Smoothness & 1.01 (0.92 to 1.11) & 0.810 \\ 
Squintability & 1.23 (1.12 to 1.38) & {\bfseries <0.001} \\ 
Dimension & 0.58 (0.45 to 0.73) & {\bfseries <0.001} \\ 
Number of jellyfish & 1.32 (1.17 to 1.50) & {\bfseries <0.001} \\ 
Maximum number of iterations & 1.06 (0.94 to 1.20) & 0.328 \\ 
\bottomrule

@@

Future work can focus on developing more efficient optimization
algorithm for noise indexes with low squintability metric, which
resemble a needle-in-a-haystack problem (Siemenn et al. 2023).
Additionally, if the index function is differentiable, automatic
differentiation can be used to implement new gradient-based optimizers
(Prince 2023).

@@

\bibitem[\citeproctext]{ref-prince2023understanding}
Prince, Simon JD. 2023. \emph{Understanding Deep Learning}. MIT press.

@@

\bibitem[\citeproctext]{ref-siemenn2023fast}
Siemenn, Alexander E, Zekun Ren, Qianxiao Li, and Tonio Buonassisi.
2023. {``Fast Bayesian Optimization of Needle-in-a-Haystack Problems
Using Zooming Memory-Based Initialization (ZoMBI).''} \emph{Npj
Computational Materials} 9 (1): 79.
